---
title: "Rolling Sales Data"
author: "Laurie Harris"
date: "February 7, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data

The dataset Rolling Sales Brooklyn was downloaded from the following website:
http://www1.nyc.gov/assets/finance/downloads/pdf/rolling_sales/rollingsales_brooklyn.xls

After analyzing the data and excluding outliers that we believed were errors, we were able to determine that a log 10 transformation would produce the most relevant results.  This scatter plot shows the relationship between total square feet and sales price for 1- 2- and 3- family homes in Brooklyn.


```{r bk, echo=FALSE}
setwd("C://Projects//6306//Rollingsales//data")
bk <- read.csv("rollingsales_brooklyn.csv",skip=4,header=TRUE)
bk$SALE.PRICE.N <- as.numeric(gsub("[^[:digit:]]","", bk$SALE.PRICE))
names(bk) <- tolower(names(bk))
bk$gross.square.feet.n <- as.numeric(gsub("[^[:digit:]]","", bk$gross.square.feet))
bk$land.square.feet.n <- as.numeric(gsub("[^[:digit:]]","", bk$land.square.feet))
bk$year.built.n <- as.numeric(gsub("[^[:digit:]]","", bk$year.built))
bk.sale <- bk[bk$sale.price.n!=0,]
bk.homes <- bk.sale[which(grepl("FAMILY",bk.sale$building.class.category)),]
bk.homes$outliers <- (log10(bk.homes$sale.price.n) <=5) + 0
bk.homes <- bk.homes[which(bk.homes$outliers==0),]
plot(log10(bk.homes$gross.square.feet.n),log10(bk.homes$sale.price.n),xlab = "Square Feet", ylab = "Sales Price")

```

